---
title: "Reproducible Research 2021: Live analysis of betting odds for tennis matches"
author:
- "Rafał Rysiejko"
- "Michał Sałach"
date: "May 2021"
output:
 prettydoc::html_pretty:
   theme: cayman
params:
 money:
   label: "Money to bet"
   value: 1000
   min: 1
 expected_return:
   label: "Expected return, if the favourite wins (fraction of money to bet)"
   value: 0.1
   min: 0.01
 adverse_return:
   label: "Accepted return, if the favourite will not win (fraction of money to bet)"
   value: -0.2
   min: -1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE,include=FALSE}
# Loading required libraries

library(viridis)      # 0.6.1
library(hrbrthemes)   # 0.8.0
library(knitr)        # 1.33
library(rmarkdown)    #2.7
library(lubridate)    #1.7.10
library(tidyverse)    # 1.3.1
library(httr)         # 1.4.2
library(rvest)        # 1.0.0
library(lubridate)    # 1.7.10
library(jsonlite)     # 1.7.2
library(eList)        # 0.2.0

```


```{r data_preparation, echo=FALSE,include=FALSE,warning=FALSE}
library(tidyverse)  # tidyverse 1.3.1


#### Data ####
data_raw <- read_csv('../data/data_270521_032950.csv') # New data 27.05
data <- data_raw

# A list of bookmakers
bookmakers <- c('eFortuna', 'STS', 'Betclic', 'Betfan', 'Pzbuk', 'Lvbet', 'Totolotek')

# Links to bookmakers websites
bookmakers_links <- c('https://www.efortuna.pl/',
                      'https://www.sts.pl/',
                      'https://www.betclic.pl/',
                      'https://betfan.pl/zaklady-bukmacherskie',
                      'https://www.pzbuk.pl/pl',
                      'https://lvbet.pl/pl/',
                      'https://www.totolotek.pl/pl')

# Creating dataframe for lookup 
bookmakers_df <- data.frame(bookmakers,bookmakers_links)


# Translating Polish tennis specific terms and countries name to English
# Loading pre-made dictionary 
dict <- read_csv('../data/translation-20210524.csv') #Change working directory to main

# Loop for detecting string matches and translating them
for (i in 1:length(dict$pl)) {
  
  data$event <- as.data.frame(sapply(data$event,gsub,pattern=dict[i,]$pl,replacement=dict[i,]$angl))

}

# Saving translated list of values as a part of dataframe and renaming it
data <- as.data.frame(do.call(cbind, data)) %>% rename(event=`sapply(data$event, gsub, pattern = dict[i, ]$pl, replacement = dict[i, ]$angl)`)

# Reshaping data to long format
data <- data %>%
  mutate(match_id = row_number(), .before = event) %>%
  mutate(match_current = if_else(if_any(contains('_games'), function(x)
    is.na(x)),
    0, 1), .after = match_time) %>%
  pivot_longer(cols = (paste0('player_1_', bookmakers)),
               names_to = 'player_1_bookmaker',
               values_to = 'player_1_odds') %>%
  pivot_longer(cols = (paste0('player_2_', bookmakers)),
               names_to = 'player_2_bookmaker',
               values_to = 'player_2_odds') %>%
  mutate(
    player_1_bookmaker = str_replace(player_1_bookmaker, 'player_1_', ''),
    player_2_bookmaker = str_replace(player_2_bookmaker, 'player_2_', '')
  ) %>%
  group_by(match_id) %>%
  mutate(
    player_1_odds_max = max(player_1_odds, na.rm = TRUE),
    player_1_odds_min = min(player_1_odds, na.rm = TRUE),
    player_2_odds_max = max(player_2_odds, na.rm = TRUE),
    player_2_odds_min = min(player_2_odds, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  filter(!(if_any(contains('_odds_'), function(x)
    is.infinite(x))))  # See the note below.

# Note: warnings signify that there are matches for which there is no offer (NAs for all
# bookmakers). It may happen that a future match has currently no betting odds, or that all 
# are crossed out by the bookmakers. We are not worried by that. The values of 
# `player_1_odds_max`, `player_1_odds_max`, `player_1_odds_max` and `player_1_odds_max` will be 
# then Inf/-Inf, and we filter them out.


# Given the expected return ((1+expected_return)*money in the case when the favourite wins),
# count the adverse return (when the favourite loses). Filter out offers when potential loss
# exceeds the adverse return and sort descending.
# (Favourite is the player whose win guarantees expected return.)

data_min_adverse <- data %>%
  group_by(match_id) %>%
  mutate(to_bet_1_if_1_favourite = (1+expected_return)*money/player_1_odds_max,
         to_bet_2_if_1_favourite = money-to_bet_1_if_1_favourite,
         win_2_bet_1 = to_bet_2_if_1_favourite*player_2_odds_max,
         win_2_bet_1_return = (win_2_bet_1-money)/money,
         to_bet_2_if_2_favourite = (1+expected_return)*money/player_2_odds_max,
         to_bet_1_if_2_favourite = money-to_bet_2_if_2_favourite,
         win_1_bet_2 = to_bet_1_if_2_favourite*player_1_odds_max,
         win_1_bet_2_return = (win_1_bet_2-money)/money,
         better_adverse_return = max(win_2_bet_1_return, win_1_bet_2_return)) %>%
  ungroup() %>% 
  filter(player_1_odds == player_1_odds_max,
         player_2_odds == player_2_odds_max,
         better_adverse_return >= adverse_return,
         to_bet_1_if_1_favourite <= money,
         to_bet_1_if_2_favourite >= 0,
         to_bet_2_if_2_favourite <= money,
         to_bet_2_if_1_favourite >= 0) %>%
  mutate(better_favourite = if_else(win_1_bet_2 > win_2_bet_1, '2', '1'),
         better_non_favourite = if_else(better_favourite == '1', '2', '1')) %>% 
  arrange(desc(better_adverse_return))


data_max_return <- data %>%
  group_by(match_id) %>%
  mutate(to_bet_1_if_2_favourite = (1+adverse_return)*money/player_1_odds_max,
         to_bet_2_if_2_favourite = money-to_bet_1_if_2_favourite,
         to_bet_2_if_1_favourite = (1+adverse_return)*money/player_2_odds_max,         
         to_bet_1_if_1_favourite = money-to_bet_2_if_1_favourite,
         win_1_bet_1 = to_bet_1_if_1_favourite*player_1_odds_max,
         win_1_bet_1_return = (win_1_bet_1-money)/money,
         win_2_bet_2 = to_bet_2_if_2_favourite*player_2_odds_max,
         win_2_bet_2_return = (win_2_bet_2-money)/money,
         better_return = max(win_1_bet_1_return, win_2_bet_2_return)) %>% 
  ungroup() %>% 
  filter(player_1_odds == player_1_odds_max,
         player_2_odds == player_2_odds_max,
         better_return >= expected_return,
         to_bet_1_if_1_favourite <= money,
         to_bet_1_if_2_favourite >= 0,
         to_bet_2_if_2_favourite <= money,
         to_bet_2_if_1_favourite >= 0) %>%
  mutate(better_favourite = if_else(win_2_bet_2 > win_1_bet_1, '2', '1'),
         better_non_favourite = if_else(better_favourite == '1', '2', '1')) %>% 
  arrange(desc(better_return))


# Creating transition dataframe for matching bookmaker and their corresponding website
book <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_bookmaker')])[1]
link <- bookmakers_df %>% filter(bookmakers==pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)


bookmakers_df %>% filter(bookmakers==pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)

```

```{r variables, echo=FALSE,include=FALSE}
# List of variable for inline referencing

#==============================================
# Best bet summary
#==============================================

value_to_bet <- round(pull(data_min_adverse[paste0('to_bet_', data_min_adverse$better_favourite[1], '_if_', data_min_adverse$better_favourite[1], '_favourite')])[1], 2)

player_to_bet_for <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1])])[1]
player_to_bet_for_nationality <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1], '_nationality')])[1]
player_to_bet_for_atp_ranking <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1], '_rank')])[1]
best_bet_bookmaker <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1], '_bookmaker')])[1]
best_bet_bookmaker_link <- bookmakers_df %>% filter(bookmakers==pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)
best_bet_betting_odds <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_favourite[1], '_odds')])[1]

value_to_bet2 <- round(pull(data_min_adverse[paste0('to_bet_', data_min_adverse$better_non_favourite[1], '_if_', data_min_adverse$better_favourite[1], '_favourite')])[1], 2)
player_to_bet_for2 <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1])])[1]
player_to_bet_for_nationality2 <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_nationality')])[1] 
player_to_bet_for_atp_ranking2 <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_rank')])[1]
best_bet_bookmaker2 <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_bookmaker')])[1]
best_bet_bookmaker_link2 <- bookmakers_df %>% filter(bookmakers==pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)
best_bet_betting_odds2 <- pull(data_min_adverse[paste0('player_', data_min_adverse$better_non_favourite[1], '_odds')])[1]

expected_return_pln <- round(pull(data_min_adverse[paste0('win_', data_min_adverse$better_non_favourite[1], '_bet_', data_min_adverse$better_favourite[1])])[1], 2)
expected_return_percentage <- round(100*pull(data_min_adverse[paste0('win_', data_min_adverse$better_non_favourite[1], '_bet_', data_min_adverse$better_favourite[1], '_return')])[1], 2)

event <- pull(data_min_adverse['event'])[1]
match_time <- pull(data_min_adverse['match_time'])[1]

```


# Best bet prediction
## Introduction 

In our project, we search for the most profitable bets to make on the tennis matches for a given moment. We consider seven popular Polish bookmakers whose betting odds are reported on an ongoing basis on flashscore.pl/tennis. We are interested in the results only (who wins) and only in the ongoing or scheduled matches for a given day. It may be safely assumed that each match will have a winner. It is also pretty always the case that for each match, there is a favorite of the bookmakers (the bookmakers do not have to be unanimous, or it may in principle happen that the odds for both players are the same - this does not cause a problem for our analysis). A favorite of a bookmaker in a given match is the player for whom offers are lower (closer to 1). There is also a favorite of a client of the bookmaker - this is the player whose win would grant the client a profit.

Given that in reality, offers for both players are greater than 1, a client does not have to bet all their money on a favorite to achieve some profit. The remaining amount of money the client would bet on a non-favorite as a form of insurance in the case of misfortune (favorite loses). A no-risk bet is, therefore, a bet in which there is a proportion of money to bet, such that a client of a bookmaker has a profit also when their favorite loses. For example, in betting, odds for a player A (the bookmaker's favorite) are 1.5, and for a player, B is 3.5, a client may bet 700 PLN on a player A and 300 PLN on a player B, granting a win of 1050 PLN (5% profit) in both cases. Such bets rather do not happen in reality, but the project aims to find the offers that come the closest to this, for any moment in time.

Our analysis is looking for the best bets to make from two angles: minimizing loss and maximizing return. Hence, we use two notions of profitability: In the first sense, we are interested in bets that would give a client minimal loss, having fixed on some level expected to return in the case of the client's favorite win. In the second sense, we are looking for bets that would give a maximal client return in their favorite's win, having fixed on some level the loss in the adverse case.
The report will therefore accept 3 meta-prameters: *money* (money to bet, defaul 1000 PLN), *expected_return* (defaul 0.1) and *adverse_return* (default -0.2).

```{r tables_calculations, echo=FALSE,include=FALSE}
# ==============================================================================
# Preparation of data for tables
# ==============================================================================
#df <- read_csv('../data_270521_001719.csv')
df <- data_raw

for (i in 1:length(dict$pl)) {
  
  df$event <- as.data.frame(sapply(df$event,gsub,pattern=dict[i,]$pl,replacement=dict[i,]$angl))
  
}
df <- as.data.frame(do.call(cbind, df)) %>% rename(event=`sapply(df$event, gsub, pattern = dict[i, ]$pl, replacement = dict[i, ]$angl)`)


df <-
  df %>% mutate(
    gender = case_when(
      str_detect(event, "Womens") ~ "W",
      str_detect(event, "WTP") ~ "W",
      TRUE ~ "M"
    ),
    match_current = if_else(if_any(contains('_games'), function(x)
      is.na(x)), 0, 1),
    .after = match_time
  )

# General table
count <- df  %>% summarise("Total count" = n())
count_gender_w <- df %>% filter(gender=="W") %>% summarise("Women matches" = n())
count_gender_m <- df %>% filter(gender=="M") %>% summarise("Men matches" = n())
count_live_yes <- df %>% filter(match_current==1) %>% summarise("Live matches" = n())
count_live_no <- df %>% filter(match_current==0) %>% summarise("Planned matches" = n())


count_bets <- df %>% select(event,player_1_eFortuna,player_1_STS,player_1_Betclic,player_1_Betfan,player_1_Lvbet,player_1_Pzbuk,player_1_Totolotek) %>% 
  filter(is.na(player_1_eFortuna) &
           is.na(player_1_STS)&
           is.na(player_1_Betclic)&
           is.na(player_1_Betfan)&
           is.na(player_1_Lvbet)&
           is.na(player_1_Pzbuk)&
           is.na( player_1_Totolotek)) %>% summarise("Number of bets"=count-n())

general_stats_table <- cbind(count,count_gender_w,count_gender_m,count_bets,count_live_yes,count_live_no)

#Bookers table
df_cnt_bet <- df %>% select(player_1_eFortuna,player_1_STS,player_1_Betclic,player_1_Betfan,player_1_Lvbet,player_1_Pzbuk,player_1_Totolotek) %>% summarise_all(funs(sum(!is.na(.))))
df_avg_bet <- df %>% select(player_1_eFortuna,player_1_STS,player_1_Betclic,player_1_Betfan,player_1_Lvbet,player_1_Pzbuk,player_1_Totolotek) %>% summarise_each(funs(mean(., na.rm = TRUE)))

bookers_table <- rbind(df_cnt_bet,df_avg_bet)
rownames(bookers_table) <- c("Bookmaker bet count","Average bet size")
colnames(bookers_table) <- c('eFortuna','STS','Betclick',"Betfan","Lvbet","Pzbuk","Totolotek")

```

### Summary statistics

```{r tables, echo=FALSE}
knitr::kable(bookers_table)
knitr::kable(general_stats_table)
```

### Best bet in case the favourite wins

Having `r money` PLN, the best bet to do right now in order to have `r 100*expected_return`% return in the case of a favorite win and minimal loss in the case of the favorite loss is to bet `r value_to_bet` PLN on `r player_to_bet_for` (`r player_to_bet_for_nationality`, ATP ranking: `r player_to_bet_for_atp_ranking`) on [`r best_bet_bookmaker`](`r best_bet_bookmaker_link`) (betting odds: `r best_bet_betting_odds`) and `r value_to_bet2` PLN on `r player_to_bet_for2` (`r player_to_bet_for_nationality2`, ATP ranking: `r player_to_bet_for_atp_ranking2`) on [`r best_bet_bookmaker2`](`r best_bet_bookmaker_link2`) (betting odds: `r best_bet_betting_odds2`, expected return: `r expected_return_pln` PLN, that is `r expected_return_percentage`%) in `r event` (starting `r match_time`).


```{r variables2, echo=FALSE,include=FALSE}
#  Creating lists of variables for inline referencing 

value_to_bet_ <- round(pull(data_max_return[paste0('to_bet_', data_max_return$better_non_favourite[1], '_if_', data_max_return$better_favourite[1], '_favourite')])[1], 2)

player_to_bet_for_ <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1])])[1]
player_to_bet_for_nationality_ <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_nationality')])[1]
player_to_bet_for_atp_ranking_ <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_rank')])[1]
best_bet_bookmaker_ <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_bookmaker')])[1]
best_bet_bookmaker_link_ <- bookmakers_df %>% filter(bookmakers==pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)
best_bet_betting_odds_ <- pull(data_max_return[paste0('player_', data_max_return$better_non_favourite[1], '_odds')])[1]

value_to_bet2_ <- round(pull(data_max_return[paste0('to_bet_', data_max_return$better_favourite[1], '_if_', data_max_return$better_favourite[1], '_favourite')])[1], 2)
player_to_bet_for2_ <- pull(data_max_return[paste0('player_', data_max_return$better_favourite[1])])[1]
player_to_bet_for_nationality2_ <- pull(data_max_return[paste0('player_', data_max_return$better_favourite[1], '_nationality')])[1]
player_to_bet_for_atp_ranking2_ <- pull(data_max_return[paste0('player_', data_max_return$better_favourite[1], '_rank')])[1]
best_bet_bookmaker2_ <- pull(data_max_return[paste0('player_', data_max_return$better_favourite[1], '_bookmaker')])[1]
best_bet_bookmaker_link2_ <- bookmakers_df %>% filter(bookmakers==pull(data_max_return[paste0('player_', data_max_return$better_favourite[1], '_bookmaker')])[1]) %>% select(bookmakers_links)
best_bet_betting_odds2_ <- pull(data_max_return[paste0('player_', data_max_return$better_favourite[1], '_odds')])[1]

expected_return_pln_ <- round(pull(data_max_return[paste0('win_', data_max_return$better_favourite[1], '_bet_', data_max_return$better_favourite[1])])[1], 2)
expected_return_percentage_ <- round(100*pull(data_max_return[paste0('win_', data_max_return$better_favourite[1], '_bet_', data_max_return$better_favourite[1], '_return')])[1], 2)

event_ <- pull(data_max_return['event'])[1]
match_time_ <- pull(data_max_return['match_time'])[1]


```

### Best bet in case the favourite loses
Having `r money` PLN, the best bet to do right now in order to have maximum`r 100*adverse_return`% return in the case of a favorite loss and maximal return in the case of the favorite win is to bet `r value_to_bet_`PLN on `r player_to_bet_for_` (`r player_to_bet_for_nationality_`, ATP ranking: `r player_to_bet_for_atp_ranking_`) on [`r best_bet_bookmaker_`](`r best_bet_bookmaker_link_`) (betting odds: `r best_bet_betting_odds_`, expected return: `r expected_return_pln_` PLN, that is `r expected_return_percentage_`%) and `r value_to_bet2_` PLN on `r player_to_bet_for2_` (`r player_to_bet_for_nationality2_`, ATP ranking: `r player_to_bet_for_atp_ranking2_`) on [`r best_bet_bookmaker2_`](`r best_bet_bookmaker_link2_`) (betting odds: `r best_bet_betting_odds2_`) in `r event_` (starting `r match_time_`)

```{r variables_top3_for_each_bookmaker, echo=FALSE,include=FALSE}
# Creating list of variable for inline referencing

# =============================================================================
# eFortuna
# Min_adverse
# =============================================================================
#Player 1
data_b1.1 <- data_min_adverse %>% filter(player_1_bookmaker == "eFortuna" | player_2_bookmaker == "eFortuna")
data_b1.1_player1_1 <- pull(data_b1.1[paste0('player_', data_b1.1$better_favourite[1])])[1]
data_b1.1_player1_2 <- pull(data_b1.1[paste0('player_', data_b1.1$better_favourite[2])])[2]
data_b1.1_player1_3 <- pull(data_b1.1[paste0('player_', data_b1.1$better_favourite[3])])[3]

# Player 2 
data_b1.1_player2_1 <- pull(data_b1.1[paste0('player_', data_b1.1$better_non_favourite[1])])[1]
data_b1.1_player2_2 <- pull(data_b1.1[paste0('player_', data_b1.1$better_non_favourite[2])])[2]
data_b1.1_player2_3 <- pull(data_b1.1[paste0('player_', data_b1.1$better_non_favourite[3])])[3]

# Event
data_b1.1_event_1 <- pull(data_b1.1['event'])[1]
data_b1.1_event_2 <- pull(data_b1.1['event'])[2]
data_b1.1_event_3 <- pull(data_b1.1['event'])[3]

# Time
data_b1.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b1.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b1.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b1.1_money1_1 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_favourite[1], '_if_', data_b1.1$better_favourite[1], '_favourite')])[1], 2)
data_b1.1_money1_2 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_favourite[2], '_if_', data_b1.1$better_favourite[1], '_favourite')])[2], 2)
data_b1.1_money1_3 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_favourite[3], '_if_', data_b1.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b1.1_money2_1 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_non_favourite[1], '_if_', data_b1.1$better_favourite[1], '_favourite')])[1], 2)
data_b1.1_money2_2 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_non_favourite[2], '_if_', data_b1.1$better_favourite[1], '_favourite')])[2], 2)
data_b1.1_money2_3 <- round(pull(data_b1.1[paste0('to_bet_', data_b1.1$better_non_favourite[3], '_if_', data_b1.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b1.1_return_1 <- round(pull(data_b1.1[paste0('win_', data_b1.1$better_non_favourite[1], '_bet_', data_b1.1$better_favourite[1])])[1], 2)
data_b1.1_return_2 <- round(pull(data_b1.1[paste0('win_', data_b1.1$better_non_favourite[2], '_bet_', data_b1.1$better_favourite[2])])[2], 2)
data_b1.1_return_3 <- round(pull(data_b1.1[paste0('win_', data_b1.1$better_non_favourite[3], '_bet_', data_b1.1$better_favourite[3])])[3], 2)

# ===========
# eFortuna
# Max return
# ========

# Max return
data_b1.2 <- data_max_return %>% filter(player_1_bookmaker == "eFortuna" | player_2_bookmaker == "eFortuna")

# Player 1 
data_b1.2_player1_1 <- pull(data_b1.2[paste0('player_', data_b1.2$better_non_favourite[1])])[1]
data_b1.2_player1_2 <- pull(data_b1.2[paste0('player_', data_b1.2$better_non_favourite[2])])[2]
data_b1.2_player1_3 <- pull(data_b1.2[paste0('player_', data_b1.2$better_non_favourite[3])])[3]

# Player 2 
data_b1.2_player2_1 <- pull(data_b1.2[paste0('player_', data_b1.2$better_favourite[1])])[1]
data_b1.2_player2_2 <- pull(data_b1.2[paste0('player_', data_b1.2$better_favourite[2])])[2]
data_b1.2_player2_3 <- pull(data_b1.2[paste0('player_', data_b1.2$better_favourite[3])])[3]

# Event
data_b1.2_event_1 <- pull(data_b1.2['event'])[1]
data_b1.2_event_2 <- pull(data_b1.2['event'])[2]
data_b1.2_event_3 <- pull(data_b1.2['event'])[3]

# Time
data_b1.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b1.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b1.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b1.2_money1_1 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_non_favourite[1], '_if_', data_b1.2$better_favourite[1], '_favourite')])[1], 2)
data_b1.2_money1_2 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_non_favourite[2], '_if_', data_b1.2$better_favourite[1], '_favourite')])[2], 2)
data_b1.2_money1_3 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_non_favourite[3], '_if_', data_b1.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b1.2_money2_1 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_favourite[1], '_if_', data_b1.2$better_favourite[1], '_favourite')])[1], 2)
data_b1.2_money2_2 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_favourite[2], '_if_', data_b1.2$better_favourite[1], '_favourite')])[2], 2)
data_b1.2_money2_3 <- round(pull(data_b1.2[paste0('to_bet_', data_b1.2$better_favourite[3], '_if_', data_b1.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b1.2_return_1 <- round(pull(data_b1.2[paste0('win_', data_b1.2$better_favourite[1], '_bet_', data_b1.2$better_favourite[1])])[1], 2)
data_b1.2_return_2 <- round(pull(data_b1.2[paste0('win_', data_b1.2$better_favourite[2], '_bet_', data_b1.2$better_favourite[2])])[2], 2)
data_b1.2_return_3 <- round(pull(data_b1.2[paste0('win_', data_b1.2$better_favourite[3], '_bet_', data_b1.2$better_favourite[3])])[3], 2)

# =============================================================================
# STS
# Min Adverse
# =============================================================================
#Player 1
data_b2.1 <- data_min_adverse %>% filter(player_1_bookmaker == "STS" | player_2_bookmaker == "STS")
data_b2.1_player1_1 <- pull(data_b2.1[paste0('player_', data_b2.1$better_favourite[1])])[1]
data_b2.1_player1_2 <- pull(data_b2.1[paste0('player_', data_b2.1$better_favourite[2])])[2]
data_b2.1_player1_3 <- pull(data_b2.1[paste0('player_', data_b2.1$better_favourite[3])])[3]

# Player 2 
data_b2.1_player2_1 <- pull(data_b2.1[paste0('player_', data_b2.1$better_non_favourite[1])])[1]
data_b2.1_player2_2 <- pull(data_b2.1[paste0('player_', data_b2.1$better_non_favourite[2])])[2]
data_b2.1_player2_3 <- pull(data_b2.1[paste0('player_', data_b2.1$better_non_favourite[3])])[3]

# Event
data_b2.1_event_1 <- pull(data_b2.1['event'])[1]
data_b2.1_event_2 <- pull(data_b2.1['event'])[2]
data_b2.1_event_3 <- pull(data_b2.1['event'])[3]

# Time
data_b2.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b2.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b2.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b2.1_money1_1 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_favourite[1], '_if_', data_b2.1$better_favourite[1], '_favourite')])[1], 2)
data_b2.1_money1_2 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_favourite[2], '_if_', data_b2.1$better_favourite[1], '_favourite')])[2], 2)
data_b2.1_money1_3 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_favourite[3], '_if_', data_b2.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b2.1_money2_1 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_non_favourite[1], '_if_', data_b2.1$better_favourite[1], '_favourite')])[1], 2)
data_b2.1_money2_2 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_non_favourite[2], '_if_', data_b2.1$better_favourite[1], '_favourite')])[2], 2)
data_b2.1_money2_3 <- round(pull(data_b2.1[paste0('to_bet_', data_b2.1$better_non_favourite[3], '_if_', data_b2.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b2.1_return_1 <- round(pull(data_b2.1[paste0('win_', data_b2.1$better_non_favourite[1], '_bet_', data_b2.1$better_favourite[1])])[1], 2)
data_b2.1_return_2 <- round(pull(data_b2.1[paste0('win_', data_b2.1$better_non_favourite[2], '_bet_', data_b2.1$better_favourite[2])])[2], 2)
data_b2.1_return_3 <- round(pull(data_b2.1[paste0('win_', data_b2.1$better_non_favourite[3], '_bet_', data_b2.1$better_favourite[3])])[3], 2)

# =============================================================================
# STS
# Max return
# =============================================================================

# Max return
data_b2.2 <- data_max_return %>% filter(player_1_bookmaker == "STS" | player_2_bookmaker == "STS")

# Player 1 
data_b2.2_player1_1 <- pull(data_b2.2[paste0('player_', data_b2.2$better_non_favourite[1])])[1]
data_b2.2_player1_2 <- pull(data_b2.2[paste0('player_', data_b2.2$better_non_favourite[2])])[2]
data_b2.2_player1_3 <- pull(data_b2.2[paste0('player_', data_b2.2$better_non_favourite[3])])[3]

# Player 2 
data_b2.2_player2_1 <- pull(data_b2.2[paste0('player_', data_b2.2$better_favourite[1])])[1]
data_b2.2_player2_2 <- pull(data_b2.2[paste0('player_', data_b2.2$better_favourite[2])])[2]
data_b2.2_player2_3 <- pull(data_b2.2[paste0('player_', data_b2.2$better_favourite[3])])[3]

# Event
data_b2.2_event_1 <- pull(data_b2.2['event'])[1]
data_b2.2_event_2 <- pull(data_b2.2['event'])[2]
data_b2.2_event_3 <- pull(data_b2.2['event'])[3]

# Time
data_b2.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b2.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b2.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b2.2_money1_1 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_non_favourite[1], '_if_', data_b2.2$better_favourite[1], '_favourite')])[1], 2)
data_b2.2_money1_2 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_non_favourite[2], '_if_', data_b2.2$better_favourite[1], '_favourite')])[2], 2)
data_b2.2_money1_3 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_non_favourite[3], '_if_', data_b2.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b2.2_money2_1 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_favourite[1], '_if_', data_b2.2$better_favourite[1], '_favourite')])[1], 2)
data_b2.2_money2_2 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_favourite[2], '_if_', data_b2.2$better_favourite[1], '_favourite')])[2], 2)
data_b2.2_money2_3 <- round(pull(data_b2.2[paste0('to_bet_', data_b2.2$better_favourite[3], '_if_', data_b2.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b2.2_return_1 <- round(pull(data_b2.2[paste0('win_', data_b2.2$better_favourite[1], '_bet_', data_b2.2$better_favourite[1])])[1], 2)
data_b2.2_return_2 <- round(pull(data_b2.2[paste0('win_', data_b2.2$better_favourite[2], '_bet_', data_b2.2$better_favourite[2])])[2], 2)
data_b2.2_return_3 <- round(pull(data_b2.2[paste0('win_', data_b2.2$better_favourite[3], '_bet_', data_b2.2$better_favourite[3])])[3], 2)


# =============================================================================
# Betclic
# Min Adverse
# =============================================================================
#Player 1
data_b3.1 <- data_min_adverse %>% filter(player_1_bookmaker == "Betclic" | player_2_bookmaker == "Betclic")
data_b3.1_player1_1 <- pull(data_b3.1[paste0('player_', data_b3.1$better_favourite[1])])[1]
data_b3.1_player1_2 <- pull(data_b3.1[paste0('player_', data_b3.1$better_favourite[2])])[2]
data_b3.1_player1_3 <- pull(data_b3.1[paste0('player_', data_b3.1$better_favourite[3])])[3]

# Player 2 
data_b3.1_player2_1 <- pull(data_b3.1[paste0('player_', data_b3.1$better_non_favourite[1])])[1]
data_b3.1_player2_2 <- pull(data_b3.1[paste0('player_', data_b3.1$better_non_favourite[2])])[2]
data_b3.1_player2_3 <- pull(data_b3.1[paste0('player_', data_b3.1$better_non_favourite[3])])[3]

# Event
data_b3.1_event_1 <- pull(data_b3.1['event'])[1]
data_b3.1_event_2 <- pull(data_b3.1['event'])[2]
data_b3.1_event_3 <- pull(data_b3.1['event'])[3]

# Time
data_b3.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b3.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b3.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b3.1_money1_1 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_favourite[1], '_if_', data_b3.1$better_favourite[1], '_favourite')])[1], 2)
data_b3.1_money1_2 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_favourite[2], '_if_', data_b3.1$better_favourite[1], '_favourite')])[2], 2)
data_b3.1_money1_3 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_favourite[3], '_if_', data_b3.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b3.1_money2_1 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_non_favourite[1], '_if_', data_b3.1$better_favourite[1], '_favourite')])[1], 2)
data_b3.1_money2_2 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_non_favourite[2], '_if_', data_b3.1$better_favourite[1], '_favourite')])[2], 2)
data_b3.1_money2_3 <- round(pull(data_b3.1[paste0('to_bet_', data_b3.1$better_non_favourite[3], '_if_', data_b3.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b3.1_return_1 <- round(pull(data_b3.1[paste0('win_', data_b3.1$better_non_favourite[1], '_bet_', data_b3.1$better_favourite[1])])[1], 2)
data_b3.1_return_2 <- round(pull(data_b3.1[paste0('win_', data_b3.1$better_non_favourite[2], '_bet_', data_b3.1$better_favourite[2])])[2], 2)
data_b3.1_return_3 <- round(pull(data_b3.1[paste0('win_', data_b3.1$better_non_favourite[3], '_bet_', data_b3.1$better_favourite[3])])[3], 2)

# =============================================================================
# Betclic
# Max return
# =============================================================================

# Max return
data_b3.2 <- data_max_return %>% filter(player_1_bookmaker == "Betclic" | player_2_bookmaker == "Betclic")

# Player 1 
data_b3.2_player1_1 <- pull(data_b3.2[paste0('player_', data_b3.2$better_non_favourite[1])])[1]
data_b3.2_player1_2 <- pull(data_b3.2[paste0('player_', data_b3.2$better_non_favourite[2])])[2]
data_b3.2_player1_3 <- pull(data_b3.2[paste0('player_', data_b3.2$better_non_favourite[3])])[3]

# Player 2 
data_b3.2_player2_1 <- pull(data_b3.2[paste0('player_', data_b3.2$better_favourite[1])])[1]
data_b3.2_player2_2 <- pull(data_b3.2[paste0('player_', data_b3.2$better_favourite[2])])[2]
data_b3.2_player2_3 <- pull(data_b3.2[paste0('player_', data_b3.2$better_favourite[3])])[3]

# Event
data_b3.2_event_1 <- pull(data_b3.2['event'])[1]
data_b3.2_event_2 <- pull(data_b3.2['event'])[2]
data_b3.2_event_3 <- pull(data_b3.2['event'])[3]

# Time
data_b3.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b3.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b3.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b3.2_money1_1 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_non_favourite[1], '_if_', data_b3.2$better_favourite[1], '_favourite')])[1], 2)
data_b3.2_money1_2 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_non_favourite[2], '_if_', data_b3.2$better_favourite[1], '_favourite')])[2], 2)
data_b3.2_money1_3 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_non_favourite[3], '_if_', data_b3.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b3.2_money2_1 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_favourite[1], '_if_', data_b3.2$better_favourite[1], '_favourite')])[1], 2)
data_b3.2_money2_2 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_favourite[2], '_if_', data_b3.2$better_favourite[1], '_favourite')])[2], 2)
data_b3.2_money2_3 <- round(pull(data_b3.2[paste0('to_bet_', data_b3.2$better_favourite[3], '_if_', data_b3.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b3.2_return_1 <- round(pull(data_b3.2[paste0('win_', data_b3.2$better_favourite[1], '_bet_', data_b3.2$better_favourite[1])])[1], 2)
data_b3.2_return_2 <- round(pull(data_b3.2[paste0('win_', data_b3.2$better_favourite[2], '_bet_', data_b3.2$better_favourite[2])])[2], 2)
data_b3.2_return_3 <- round(pull(data_b3.2[paste0('win_', data_b3.2$better_favourite[3], '_bet_', data_b3.2$better_favourite[3])])[3], 2)
# =============================================================================


# =============================================================================
# Betfan
# Min Adverse
# =============================================================================
#Player 1
data_b4.1 <- data_min_adverse %>% filter(player_1_bookmaker == "Betfan" | player_2_bookmaker == "Betfan")
data_b4.1_player1_1 <- pull(data_b4.1[paste0('player_', data_b4.1$better_favourite[1])])[1]
data_b4.1_player1_2 <- pull(data_b4.1[paste0('player_', data_b4.1$better_favourite[2])])[2]
data_b4.1_player1_3 <- pull(data_b4.1[paste0('player_', data_b4.1$better_favourite[3])])[3]

# Player 2 
data_b4.1_player2_1 <- pull(data_b4.1[paste0('player_', data_b4.1$better_non_favourite[1])])[1]
data_b4.1_player2_2 <- pull(data_b4.1[paste0('player_', data_b4.1$better_non_favourite[2])])[2]
data_b4.1_player2_3 <- pull(data_b4.1[paste0('player_', data_b4.1$better_non_favourite[3])])[3]

# Event
data_b4.1_event_1 <- pull(data_b4.1['event'])[1]
data_b4.1_event_2 <- pull(data_b4.1['event'])[2]
data_b4.1_event_3 <- pull(data_b4.1['event'])[3]

# Time
data_b4.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b4.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b4.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b4.1_money1_1 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_favourite[1], '_if_', data_b4.1$better_favourite[1], '_favourite')])[1], 2)
data_b4.1_money1_2 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_favourite[2], '_if_', data_b4.1$better_favourite[1], '_favourite')])[2], 2)
data_b4.1_money1_3 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_favourite[3], '_if_', data_b4.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b4.1_money2_1 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_non_favourite[1], '_if_', data_b4.1$better_favourite[1], '_favourite')])[1], 2)
data_b4.1_money2_2 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_non_favourite[2], '_if_', data_b4.1$better_favourite[1], '_favourite')])[2], 2)
data_b4.1_money2_3 <- round(pull(data_b4.1[paste0('to_bet_', data_b4.1$better_non_favourite[3], '_if_', data_b4.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b4.1_return_1 <- round(pull(data_b4.1[paste0('win_', data_b4.1$better_non_favourite[1], '_bet_', data_b4.1$better_favourite[1])])[1], 2)
data_b4.1_return_2 <- round(pull(data_b4.1[paste0('win_', data_b4.1$better_non_favourite[2], '_bet_', data_b4.1$better_favourite[2])])[2], 2)
data_b4.1_return_3 <- round(pull(data_b4.1[paste0('win_', data_b4.1$better_non_favourite[3], '_bet_', data_b4.1$better_favourite[3])])[3], 2)

# =============================================================================
# Betfan
# Max return
# =============================================================================

# Max return
data_b4.2 <- data_max_return %>% filter(player_1_bookmaker == "Betfan" | player_2_bookmaker == "Betfan")

# Player 1 
data_b4.2_player1_1 <- pull(data_b4.2[paste0('player_', data_b4.2$better_non_favourite[1])])[1]
data_b4.2_player1_2 <- pull(data_b4.2[paste0('player_', data_b4.2$better_non_favourite[2])])[2]
data_b4.2_player1_3 <- pull(data_b4.2[paste0('player_', data_b4.2$better_non_favourite[3])])[3]

# Player 2 
data_b4.2_player2_1 <- pull(data_b4.2[paste0('player_', data_b4.2$better_favourite[1])])[1]
data_b4.2_player2_2 <- pull(data_b4.2[paste0('player_', data_b4.2$better_favourite[2])])[2]
data_b4.2_player2_3 <- pull(data_b4.2[paste0('player_', data_b4.2$better_favourite[3])])[3]

# Event
data_b4.2_event_1 <- pull(data_b4.2['event'])[1]
data_b4.2_event_2 <- pull(data_b4.2['event'])[2]
data_b4.2_event_3 <- pull(data_b4.2['event'])[3]

# Time
data_b4.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b4.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b4.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b4.2_money1_1 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_non_favourite[1], '_if_', data_b4.2$better_favourite[1], '_favourite')])[1], 2)
data_b4.2_money1_2 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_non_favourite[2], '_if_', data_b4.2$better_favourite[1], '_favourite')])[2], 2)
data_b4.2_money1_3 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_non_favourite[3], '_if_', data_b4.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b4.2_money2_1 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_favourite[1], '_if_', data_b4.2$better_favourite[1], '_favourite')])[1], 2)
data_b4.2_money2_2 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_favourite[2], '_if_', data_b4.2$better_favourite[1], '_favourite')])[2], 2)
data_b4.2_money2_3 <- round(pull(data_b4.2[paste0('to_bet_', data_b4.2$better_favourite[3], '_if_', data_b4.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b4.2_return_1 <- round(pull(data_b4.2[paste0('win_', data_b4.2$better_favourite[1], '_bet_', data_b4.2$better_favourite[1])])[1], 2)
data_b4.2_return_2 <- round(pull(data_b4.2[paste0('win_', data_b4.2$better_favourite[2], '_bet_', data_b4.2$better_favourite[2])])[2], 2)
data_b4.2_return_3 <- round(pull(data_b4.2[paste0('win_', data_b4.2$better_favourite[3], '_bet_', data_b4.2$better_favourite[3])])[3], 2)


# =============================================================================
# Pzbuk
# Min Adverse
# =============================================================================
#Player 1
data_b5.1 <- data_min_adverse %>% filter(player_1_bookmaker == "Pzbuk" | player_2_bookmaker == "Pzbuk")
data_b5.1_player1_1 <- pull(data_b5.1[paste0('player_', data_b5.1$better_favourite[1])])[1]
data_b5.1_player1_2 <- pull(data_b5.1[paste0('player_', data_b5.1$better_favourite[2])])[2]
data_b5.1_player1_3 <- pull(data_b5.1[paste0('player_', data_b5.1$better_favourite[3])])[3]

# Player 2 
data_b5.1_player2_1 <- pull(data_b5.1[paste0('player_', data_b5.1$better_non_favourite[1])])[1]
data_b5.1_player2_2 <- pull(data_b5.1[paste0('player_', data_b5.1$better_non_favourite[2])])[2]
data_b5.1_player2_3 <- pull(data_b5.1[paste0('player_', data_b5.1$better_non_favourite[3])])[3]

# Event
data_b5.1_event_1 <- pull(data_b5.1['event'])[1]
data_b5.1_event_2 <- pull(data_b5.1['event'])[2]
data_b5.1_event_3 <- pull(data_b5.1['event'])[3]

# Time
data_b5.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b5.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b5.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b5.1_money1_1 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_favourite[1], '_if_', data_b5.1$better_favourite[1], '_favourite')])[1], 2)
data_b5.1_money1_2 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_favourite[2], '_if_', data_b5.1$better_favourite[1], '_favourite')])[2], 2)
data_b5.1_money1_3 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_favourite[3], '_if_', data_b5.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b5.1_money2_1 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_non_favourite[1], '_if_', data_b5.1$better_favourite[1], '_favourite')])[1], 2)
data_b5.1_money2_2 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_non_favourite[2], '_if_', data_b5.1$better_favourite[1], '_favourite')])[2], 2)
data_b5.1_money2_3 <- round(pull(data_b5.1[paste0('to_bet_', data_b5.1$better_non_favourite[3], '_if_', data_b5.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b5.1_return_1 <- round(pull(data_b5.1[paste0('win_', data_b5.1$better_non_favourite[1], '_bet_', data_b5.1$better_favourite[1])])[1], 2)
data_b5.1_return_2 <- round(pull(data_b5.1[paste0('win_', data_b5.1$better_non_favourite[2], '_bet_', data_b5.1$better_favourite[2])])[2], 2)
data_b5.1_return_3 <- round(pull(data_b5.1[paste0('win_', data_b5.1$better_non_favourite[3], '_bet_', data_b5.1$better_favourite[3])])[3], 2)

# =============================================================================
# Pzbuk
# Max return
# =============================================================================

# Max return
data_b5.2 <- data_max_return %>% filter(player_1_bookmaker == "Pzbuk" | player_2_bookmaker == "Pzbuk")

# Player 1 
data_b5.2_player1_1 <- pull(data_b5.2[paste0('player_', data_b5.2$better_non_favourite[1])])[1]
data_b5.2_player1_2 <- pull(data_b5.2[paste0('player_', data_b5.2$better_non_favourite[2])])[2]
data_b5.2_player1_3 <- pull(data_b5.2[paste0('player_', data_b5.2$better_non_favourite[3])])[3]

# Player 2 
data_b5.2_player2_1 <- pull(data_b5.2[paste0('player_', data_b5.2$better_favourite[1])])[1]
data_b5.2_player2_2 <- pull(data_b5.2[paste0('player_', data_b5.2$better_favourite[2])])[2]
data_b5.2_player2_3 <- pull(data_b5.2[paste0('player_', data_b5.2$better_favourite[3])])[3]

# Event
data_b5.2_event_1 <- pull(data_b5.2['event'])[1]
data_b5.2_event_2 <- pull(data_b5.2['event'])[2]
data_b5.2_event_3 <- pull(data_b5.2['event'])[3]

# Time
data_b5.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b5.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b5.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b5.2_money1_1 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_non_favourite[1], '_if_', data_b5.2$better_favourite[1], '_favourite')])[1], 2)
data_b5.2_money1_2 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_non_favourite[2], '_if_', data_b5.2$better_favourite[1], '_favourite')])[2], 2)
data_b5.2_money1_3 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_non_favourite[3], '_if_', data_b5.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b5.2_money2_1 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_favourite[1], '_if_', data_b5.2$better_favourite[1], '_favourite')])[1], 2)
data_b5.2_money2_2 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_favourite[2], '_if_', data_b5.2$better_favourite[1], '_favourite')])[2], 2)
data_b5.2_money2_3 <- round(pull(data_b5.2[paste0('to_bet_', data_b5.2$better_favourite[3], '_if_', data_b5.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b5.2_return_1 <- round(pull(data_b5.2[paste0('win_', data_b5.2$better_favourite[1], '_bet_', data_b5.2$better_favourite[1])])[1], 2)
data_b5.2_return_2 <- round(pull(data_b5.2[paste0('win_', data_b5.2$better_favourite[2], '_bet_', data_b5.2$better_favourite[2])])[2], 2)
data_b5.2_return_3 <- round(pull(data_b5.2[paste0('win_', data_b5.2$better_favourite[3], '_bet_', data_b5.2$better_favourite[3])])[3], 2)


# =============================================================================
# Lvbet
# Min Adverse
# =============================================================================
#Player 1
data_b6.1 <- data_min_adverse %>% filter(player_1_bookmaker == "Lvbet" | player_2_bookmaker == "Lvbet")
data_b6.1_player1_1 <- pull(data_b6.1[paste0('player_', data_b6.1$better_favourite[1])])[1]
data_b6.1_player1_2 <- pull(data_b6.1[paste0('player_', data_b6.1$better_favourite[2])])[2]
data_b6.1_player1_3 <- pull(data_b6.1[paste0('player_', data_b6.1$better_favourite[3])])[3]

# Player 2 
data_b6.1_player2_1 <- pull(data_b6.1[paste0('player_', data_b6.1$better_non_favourite[1])])[1]
data_b6.1_player2_2 <- pull(data_b6.1[paste0('player_', data_b6.1$better_non_favourite[2])])[2]
data_b6.1_player2_3 <- pull(data_b6.1[paste0('player_', data_b6.1$better_non_favourite[3])])[3]

# Event
data_b6.1_event_1 <- pull(data_b6.1['event'])[1]
data_b6.1_event_2 <- pull(data_b6.1['event'])[2]
data_b6.1_event_3 <- pull(data_b6.1['event'])[3]

# Time
data_b6.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b6.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b6.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b6.1_money1_1 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_favourite[1], '_if_', data_b6.1$better_favourite[1], '_favourite')])[1], 2)
data_b6.1_money1_2 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_favourite[2], '_if_', data_b6.1$better_favourite[1], '_favourite')])[2], 2)
data_b6.1_money1_3 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_favourite[3], '_if_', data_b6.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b6.1_money2_1 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_non_favourite[1], '_if_', data_b6.1$better_favourite[1], '_favourite')])[1], 2)
data_b6.1_money2_2 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_non_favourite[2], '_if_', data_b6.1$better_favourite[1], '_favourite')])[2], 2)
data_b6.1_money2_3 <- round(pull(data_b6.1[paste0('to_bet_', data_b6.1$better_non_favourite[3], '_if_', data_b6.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b6.1_return_1 <- round(pull(data_b6.1[paste0('win_', data_b6.1$better_non_favourite[1], '_bet_', data_b6.1$better_favourite[1])])[1], 2)
data_b6.1_return_2 <- round(pull(data_b6.1[paste0('win_', data_b6.1$better_non_favourite[2], '_bet_', data_b6.1$better_favourite[2])])[2], 2)
data_b6.1_return_3 <- round(pull(data_b6.1[paste0('win_', data_b6.1$better_non_favourite[3], '_bet_', data_b6.1$better_favourite[3])])[3], 2)

# =============================================================================
# Lvbet
# Max return
# =============================================================================

# Max return
data_b6.2 <- data_max_return %>% filter(player_1_bookmaker == "Lvbet" | player_2_bookmaker == "Lvbet")

# Player 1 
data_b6.2_player1_1 <- pull(data_b6.2[paste0('player_', data_b6.2$better_non_favourite[1])])[1]
data_b6.2_player1_2 <- pull(data_b6.2[paste0('player_', data_b6.2$better_non_favourite[2])])[2]
data_b6.2_player1_3 <- pull(data_b6.2[paste0('player_', data_b6.2$better_non_favourite[3])])[3]

# Player 2 
data_b6.2_player2_1 <- pull(data_b6.2[paste0('player_', data_b6.2$better_favourite[1])])[1]
data_b6.2_player2_2 <- pull(data_b6.2[paste0('player_', data_b6.2$better_favourite[2])])[2]
data_b6.2_player2_3 <- pull(data_b6.2[paste0('player_', data_b6.2$better_favourite[3])])[3]

# Event
data_b6.2_event_1 <- pull(data_b6.2['event'])[1]
data_b6.2_event_2 <- pull(data_b6.2['event'])[2]
data_b6.2_event_3 <- pull(data_b6.2['event'])[3]

# Time
data_b6.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b6.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b6.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b6.2_money1_1 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_non_favourite[1], '_if_', data_b6.2$better_favourite[1], '_favourite')])[1], 2)
data_b6.2_money1_2 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_non_favourite[2], '_if_', data_b6.2$better_favourite[1], '_favourite')])[2], 2)
data_b6.2_money1_3 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_non_favourite[3], '_if_', data_b6.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b6.2_money2_1 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_favourite[1], '_if_', data_b6.2$better_favourite[1], '_favourite')])[1], 2)
data_b6.2_money2_2 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_favourite[2], '_if_', data_b6.2$better_favourite[1], '_favourite')])[2], 2)
data_b6.2_money2_3 <- round(pull(data_b6.2[paste0('to_bet_', data_b6.2$better_favourite[3], '_if_', data_b6.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b6.2_return_1 <- round(pull(data_b6.2[paste0('win_', data_b6.2$better_favourite[1], '_bet_', data_b6.2$better_favourite[1])])[1], 2)
data_b6.2_return_2 <- round(pull(data_b6.2[paste0('win_', data_b6.2$better_favourite[2], '_bet_', data_b6.2$better_favourite[2])])[2], 2)
data_b6.2_return_3 <- round(pull(data_b6.2[paste0('win_', data_b6.2$better_favourite[3], '_bet_', data_b6.2$better_favourite[3])])[3], 2)



# =============================================================================
# Totolotek
# Min Adverse
# =============================================================================
#Player 1
data_b7.1 <- data_min_adverse %>% filter(player_1_bookmaker == "Totolotek" | player_2_bookmaker == "Totolotek")
data_b7.1_player1_1 <- pull(data_b7.1[paste0('player_', data_b7.1$better_favourite[1])])[1]
data_b7.1_player1_2 <- pull(data_b7.1[paste0('player_', data_b7.1$better_favourite[2])])[2]
data_b7.1_player1_3 <- pull(data_b7.1[paste0('player_', data_b7.1$better_favourite[3])])[3]

# Player 2 
data_b7.1_player2_1 <- pull(data_b7.1[paste0('player_', data_b7.1$better_non_favourite[1])])[1]
data_b7.1_player2_2 <- pull(data_b7.1[paste0('player_', data_b7.1$better_non_favourite[2])])[2]
data_b7.1_player2_3 <- pull(data_b7.1[paste0('player_', data_b7.1$better_non_favourite[3])])[3]

# Event
data_b7.1_event_1 <- pull(data_b7.1['event'])[1]
data_b7.1_event_2 <- pull(data_b7.1['event'])[2]
data_b7.1_event_3 <- pull(data_b7.1['event'])[3]

# Time
data_b7.1_time_1 <- pull(data_max_return['match_time'])[1]
data_b7.1_time_2 <- pull(data_max_return['match_time'])[2]
data_b7.1_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet 1
data_b7.1_money1_1 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_favourite[1], '_if_', data_b7.1$better_favourite[1], '_favourite')])[1], 2)
data_b7.1_money1_2 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_favourite[2], '_if_', data_b7.1$better_favourite[1], '_favourite')])[2], 2)
data_b7.1_money1_3 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_favourite[3], '_if_', data_b7.1$better_favourite[1], '_favourite')])[3], 2)

# Money to bet 2
data_b7.1_money2_1 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_non_favourite[1], '_if_', data_b7.1$better_favourite[1], '_favourite')])[1], 2)
data_b7.1_money2_2 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_non_favourite[2], '_if_', data_b7.1$better_favourite[1], '_favourite')])[2], 2)
data_b7.1_money2_3 <- round(pull(data_b7.1[paste0('to_bet_', data_b7.1$better_non_favourite[3], '_if_', data_b7.1$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b7.1_return_1 <- round(pull(data_b7.1[paste0('win_', data_b7.1$better_non_favourite[1], '_bet_', data_b7.1$better_favourite[1])])[1], 2)
data_b7.1_return_2 <- round(pull(data_b7.1[paste0('win_', data_b7.1$better_non_favourite[2], '_bet_', data_b7.1$better_favourite[2])])[2], 2)
data_b7.1_return_3 <- round(pull(data_b7.1[paste0('win_', data_b7.1$better_non_favourite[3], '_bet_', data_b7.1$better_favourite[3])])[3], 2)

# =============================================================================
# Totolotek
# Max return
# =============================================================================

# Max return
data_b7.2 <- data_max_return %>% filter(player_1_bookmaker == "Totolotek" | player_2_bookmaker == "Totolotek")

# Player 1 
data_b7.2_player1_1 <- pull(data_b7.2[paste0('player_', data_b7.2$better_non_favourite[1])])[1]
data_b7.2_player1_2 <- pull(data_b7.2[paste0('player_', data_b7.2$better_non_favourite[2])])[2]
data_b7.2_player1_3 <- pull(data_b7.2[paste0('player_', data_b7.2$better_non_favourite[3])])[3]

# Player 2 
data_b7.2_player2_1 <- pull(data_b7.2[paste0('player_', data_b7.2$better_favourite[1])])[1]
data_b7.2_player2_2 <- pull(data_b7.2[paste0('player_', data_b7.2$better_favourite[2])])[2]
data_b7.2_player2_3 <- pull(data_b7.2[paste0('player_', data_b7.2$better_favourite[3])])[3]

# Event
data_b7.2_event_1 <- pull(data_b7.2['event'])[1]
data_b7.2_event_2 <- pull(data_b7.2['event'])[2]
data_b7.2_event_3 <- pull(data_b7.2['event'])[3]

# Time
data_b7.2_time_1 <- pull(data_max_return['match_time'])[1]
data_b7.2_time_2 <- pull(data_max_return['match_time'])[2]
data_b7.2_time_3 <- pull(data_max_return['match_time'])[3]

# Money to bet player 1
data_b7.2_money1_1 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_non_favourite[1], '_if_', data_b7.2$better_favourite[1], '_favourite')])[1], 2)
data_b7.2_money1_2 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_non_favourite[2], '_if_', data_b7.2$better_favourite[1], '_favourite')])[2], 2)
data_b7.2_money1_3 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_non_favourite[3], '_if_', data_b7.2$better_favourite[1], '_favourite')])[3], 2)

# Money to bet player 2
data_b7.2_money2_1 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_favourite[1], '_if_', data_b7.2$better_favourite[1], '_favourite')])[1], 2)
data_b7.2_money2_2 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_favourite[2], '_if_', data_b7.2$better_favourite[1], '_favourite')])[2], 2)
data_b7.2_money2_3 <- round(pull(data_b7.2[paste0('to_bet_', data_b7.2$better_favourite[3], '_if_', data_b7.2$better_favourite[1], '_favourite')])[3], 2)

# Expected return
data_b7.2_return_1 <- round(pull(data_b7.2[paste0('win_', data_b7.2$better_favourite[1], '_bet_', data_b7.2$better_favourite[1])])[1], 2)
data_b7.2_return_2 <- round(pull(data_b7.2[paste0('win_', data_b7.2$better_favourite[2], '_bet_', data_b7.2$better_favourite[2])])[2], 2)
data_b7.2_return_3 <- round(pull(data_b7.2[paste0('win_', data_b7.2$better_favourite[3], '_bet_', data_b7.2$better_favourite[3])])[3], 2)


```

### Top 3 bets for each bookmaker
**eFortuna**

*Minimum adverse*

1. Bet `r data_b1.1_money1_1` PLN for `r data_b1.1_player1_1` and `r data_b1.1_money2_1` PLN for `r data_b1.1_player2_1` in `r data_b1.1_event_1` (starting `r data_b1.1_time_1`) with an expected return of `r data_b1.1_return_1`

2. Bet `r data_b1.1_money1_2` PLN for `r data_b1.1_player1_2` and `r data_b1.1_money2_2` PLN for `r data_b1.1_player2_2` in `r data_b1.1_event_2` (starting `r data_b1.1_time_2`) with an expected return of `r data_b1.1_return_2`

3. Bet `r data_b1.1_money1_3` PLN for `r data_b1.1_player1_3` and `r data_b1.1_money2_3` PLN for `r data_b1.1_player2_3` in `r data_b1.1_event_3` (starting `r data_b1.1_time_3`) with an expected return of `r data_b1.1_return_3`

*Maximum return*

1. Bet `r data_b1.2_money1_1` PLN for `r data_b1.2_player1_1` and `r data_b1.2_money2_1` PLN for `r data_b1.2_player2_1` in `r data_b1.2_event_1` (starting `r data_b1.2_time_1`) with an expected return of `r data_b1.2_return_1`

2. Bet `r data_b1.2_money1_2` PLN for `r data_b1.2_player1_2` and `r data_b1.2_money2_2` PLN for `r data_b1.2_player2_2`in `r data_b1.2_event_2` (starting `r data_b1.2_time_2`) with an expected return of `r data_b1.2_return_2`

3. Bet `r data_b1.2_money1_3` PLN for `r data_b1.2_player1_3` and `r data_b1.2_money2_3` PLN for `r data_b1.2_player2_3` in `r data_b1.2_event_3` (starting `r data_b1.2_time_3`) with an expected return of `r data_b1.2_return_3`


**STS**

*Minimum adverse*

1. Bet `r data_b2.1_money1_1` PLN for `r data_b2.1_player1_1` and `r data_b2.1_money2_1` PLN for `r data_b2.1_player2_1` in `r data_b2.1_event_1` (starting `r data_b2.1_time_1`) with an expected return of `r data_b2.1_return_1`

2. Bet `r data_b2.1_money1_2` PLN for `r data_b2.1_player1_2` and `r data_b2.1_money2_2` PLN for `r data_b2.1_player2_2` in `r data_b2.1_event_2` (starting `r data_b2.1_time_2`) with an expected return of `r data_b2.1_return_2`

3. Bet `r data_b2.1_money1_3` PLN for `r data_b2.1_player1_3` and `r data_b2.1_money2_3` PLN for `r data_b2.1_player2_3` in `r data_b2.1_event_3` (starting `r data_b2.1_time_3`) with an expected return of `r data_b2.1_return_3`

*Maximum return*

1. Bet `r data_b2.2_money1_1` PLN for `r data_b2.2_player1_1` and `r data_b2.2_money2_1` PLN for `r data_b2.2_player2_1` in `r data_b2.2_event_1` (starting `r data_b2.2_time_1`) with an expected return of `r data_b2.2_return_1`

2. Bet `r data_b2.2_money1_2` PLN for `r data_b2.2_player1_2` and `r data_b2.2_money2_2` PLN for `r data_b2.2_player2_2`in `r data_b2.2_event_2` (starting `r data_b2.2_time_2`) with an expected return of `r data_b2.2_return_2`

3. Bet `r data_b2.2_money1_3` PLN for `r data_b2.2_player1_3` and `r data_b2.2_money2_3` PLN for `r data_b2.2_player2_3` in `r data_b2.2_event_3` (starting `r data_b2.2_time_3`) with an expected return of `r data_b2.2_return_3`

**Betclick**

*Minimum adverse*

1. Bet `r data_b3.1_money1_1` PLN for `r data_b3.1_player1_1` and `r data_b3.1_money2_1` PLN for `r data_b3.1_player2_1` in `r data_b3.1_event_1` (starting `r data_b3.1_time_1`) with an expected return of `r data_b3.1_return_1`

2. Bet `r data_b3.1_money1_2` PLN for `r data_b3.1_player1_2` and `r data_b3.1_money2_2` PLN for `r data_b3.1_player2_2` in `r data_b3.1_event_2` (starting `r data_b3.1_time_2`) with an expected return of `r data_b3.1_return_2`

3. Bet `r data_b3.1_money1_3` PLN for `r data_b3.1_player1_3` and `r data_b3.1_money2_3` PLN for `r data_b3.1_player2_3` in `r data_b3.1_event_3` (starting `r data_b3.1_time_3`) with an expected return of `r data_b3.1_return_3`

*Maximum return*

1. Bet `r data_b3.2_money1_1` PLN for `r data_b3.2_player1_1` and `r data_b3.2_money2_1` PLN for `r data_b3.2_player2_1` in `r data_b3.2_event_1` (starting `r data_b3.2_time_1`) with an expected return of `r data_b3.2_return_1`

2. Bet `r data_b3.2_money1_2` PLN for `r data_b3.2_player1_2` and `r data_b3.2_money2_2` PLN for `r data_b3.2_player2_2`in `r data_b3.2_event_2` (starting `r data_b3.2_time_2`) with an expected return of `r data_b3.2_return_2`

3. Bet `r data_b3.2_money1_3` PLN for `r data_b3.2_player1_3` and `r data_b3.2_money2_3` PLN for `r data_b3.2_player2_3` in `r data_b3.2_event_3` (starting `r data_b3.2_time_3`) with an expected return of `r data_b3.2_return_3`

**Betfan**

*Minimum adverse*

1. Bet `r data_b4.1_money1_1` PLN for `r data_b4.1_player1_1` and `r data_b4.1_money2_1` PLN for `r data_b4.1_player2_1` in `r data_b4.1_event_1` (starting `r data_b4.1_time_1`) with an expected return of `r data_b4.1_return_1`

2. Bet `r data_b4.1_money1_2` PLN for `r data_b4.1_player1_2` and `r data_b4.1_money2_2` PLN for `r data_b4.1_player2_2` in `r data_b4.1_event_2` (starting `r data_b4.1_time_2`) with an expected return of `r data_b4.1_return_2`

3. Bet `r data_b4.1_money1_3` PLN for `r data_b4.1_player1_3` and `r data_b4.1_money2_3` PLN for `r data_b4.1_player2_3` in `r data_b4.1_event_3` (starting `r data_b4.1_time_3`) with an expected return of `r data_b4.1_return_3`

*Maximum return*

1. Bet `r data_b4.2_money1_1` PLN for `r data_b4.2_player1_1` and `r data_b4.2_money2_1` PLN for `r data_b4.2_player2_1` in `r data_b4.2_event_1` (starting `r data_b4.2_time_1`) with an expected return of `r data_b4.2_return_1`

2. Bet `r data_b4.2_money1_2` PLN for `r data_b4.2_player1_2` and `r data_b4.2_money2_2` PLN for `r data_b4.2_player2_2`in `r data_b4.2_event_2` (starting `r data_b4.2_time_2`) with an expected return of `r data_b4.2_return_2`

3. Bet `r data_b4.2_money1_3` PLN for `r data_b4.2_player1_3` and `r data_b4.2_money2_3` PLN for `r data_b4.2_player2_3` in `r data_b4.2_event_3` (starting `r data_b4.2_time_3`) with an expected return of `r data_b4.2_return_3`


**Pzbuk**

*Minimum adverse*

1. Bet `r data_b5.1_money1_1` PLN for `r data_b5.1_player1_1` and `r data_b5.1_money2_1` PLN for `r data_b5.1_player2_1` in `r data_b5.1_event_1` (starting `r data_b5.1_time_1`) with an expected return of `r data_b5.1_return_1`

2. Bet `r data_b5.1_money1_2` PLN for `r data_b5.1_player1_2` and `r data_b5.1_money2_2` PLN for `r data_b5.1_player2_2` in `r data_b5.1_event_2` (starting `r data_b5.1_time_2`) with an expected return of `r data_b5.1_return_2`

3. Bet `r data_b5.1_money1_3` PLN for `r data_b5.1_player1_3` and `r data_b5.1_money2_3` PLN for `r data_b5.1_player2_3` in `r data_b5.1_event_3` (starting `r data_b5.1_time_3`) with an expected return of `r data_b5.1_return_3`

*Maximum return*

1. Bet `r data_b5.2_money1_1` PLN for `r data_b5.2_player1_1` and `r data_b5.2_money2_1` PLN for `r data_b5.2_player2_1` in `r data_b5.2_event_1` (starting `r data_b5.2_time_1`) with an expected return of `r data_b5.2_return_1`

2. Bet `r data_b5.2_money1_2` PLN for `r data_b5.2_player1_2` and `r data_b5.2_money2_2` PLN for `r data_b5.2_player2_2`in `r data_b5.2_event_2` (starting `r data_b5.2_time_2`) with an expected return of `r data_b5.2_return_2`

3. Bet `r data_b5.2_money1_3` PLN for `r data_b5.2_player1_3` and `r data_b5.2_money2_3` PLN for `r data_b5.2_player2_3` in `r data_b5.2_event_3` (starting `r data_b5.2_time_3`) with an expected return of `r data_b5.2_return_3`


**Lvbet**

*Minimum adverse*

1. Bet `r data_b6.1_money1_1` PLN for `r data_b6.1_player1_1` and `r data_b6.1_money2_1` PLN for `r data_b6.1_player2_1` in `r data_b6.1_event_1` (starting `r data_b6.1_time_1`) with an expected return of `r data_b6.1_return_1`

2. Bet `r data_b6.1_money1_2` PLN for `r data_b6.1_player1_2` and `r data_b6.1_money2_2` PLN for `r data_b6.1_player2_2` in `r data_b6.1_event_2` (starting `r data_b6.1_time_2`) with an expected return of `r data_b6.1_return_2`

3. Bet `r data_b6.1_money1_3` PLN for `r data_b6.1_player1_3` and `r data_b6.1_money2_3` PLN for `r data_b6.1_player2_3` in `r data_b6.1_event_3` (starting `r data_b6.1_time_3`) with an expected return of `r data_b6.1_return_3`

*Maximum return*

1. Bet `r data_b6.2_money1_1` PLN for `r data_b6.2_player1_1` and `r data_b6.2_money2_1` PLN for `r data_b6.2_player2_1` in `r data_b6.2_event_1` (starting `r data_b6.2_time_1`) with an expected return of `r data_b6.2_return_1`

2. Bet `r data_b6.2_money1_2` PLN for `r data_b6.2_player1_2` and `r data_b6.2_money2_2` PLN for `r data_b6.2_player2_2`in `r data_b6.2_event_2` (starting `r data_b6.2_time_2`) with an expected return of `r data_b6.2_return_2`

3. Bet `r data_b6.2_money1_3` PLN for `r data_b6.2_player1_3` and `r data_b6.2_money2_3` PLN for `r data_b6.2_player2_3` in `r data_b6.2_event_3` (starting `r data_b6.2_time_3`) with an expected return of `r data_b6.2_return_3`

**Totolotek**

*Minimum adverse*

1. Bet `r data_b7.1_money1_1` PLN for `r data_b7.1_player1_1` and `r data_b7.1_money2_1` PLN for `r data_b7.1_player2_1` in `r data_b7.1_event_1` (starting `r data_b7.1_time_1`) with an expected return of `r data_b7.1_return_1`

2. Bet `r data_b7.1_money1_2` PLN for `r data_b7.1_player1_2` and `r data_b7.1_money2_2` PLN for `r data_b7.1_player2_2` in `r data_b7.1_event_2` (starting `r data_b7.1_time_2`) with an expected return of `r data_b7.1_return_2`

3. Bet `r data_b7.1_money1_3` PLN for `r data_b7.1_player1_3` and `r data_b7.1_money2_3` PLN for `r data_b7.1_player2_3` in `r data_b7.1_event_3` (starting `r data_b7.1_time_3`) with an expected return of `r data_b7.1_return_3`

*Maximum return*

1. Bet `r data_b7.2_money1_1` PLN for `r data_b7.2_player1_1` and `r data_b7.2_money2_1` PLN for `r data_b7.2_player2_1` in `r data_b7.2_event_1` (starting `r data_b7.2_time_1`) with an expected return of `r data_b7.2_return_1`

2. Bet `r data_b7.2_money1_2` PLN for `r data_b7.2_player1_2` and `r data_b7.2_money2_2` PLN for `r data_b7.2_player2_2`in `r data_b7.2_event_2` (starting `r data_b7.2_time_2`) with an expected return of `r data_b7.2_return_2`

3. Bet `r data_b7.2_money1_3` PLN for `r data_b7.2_player1_3` and `r data_b7.2_money2_3` PLN for `r data_b7.2_player2_3` in `r data_b7.2_event_3` (starting `r data_b7.2_time_3`) with an expected return of `r data_b7.2_return_3`



**Disclaimer**

*Please note, that online betting is a gambling entertainment vehicle, and that it carries with it a certain degree of financial risk. Players should be aware of this risk, and govern themselves accordingly.*
